---
title: "ONT-MLST Analysis Report"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    toc_depth: 2
    df_print: paged
params:
  summary: ""
  long: ""
  version: "dev"
  commit: "no-git"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE,
  fig.width = 10, fig.height = 5, dpi = 150, out.width = "100%"
)
suppressPackageStartupMessages({
  library(tidyverse)
  library(DT)
  library(plotly)
  library(knitr)
  library(kableExtra)
  library(htmltools)
})

theme_set(
  theme_minimal(base_size = 13) +
  theme(plot.title  = element_text(face = "bold", size = 15),
        legend.position = "right",
        panel.grid.minor = element_blank())
)
```

```{r load-data, include=FALSE}
summary_df <- read_tsv(params$summary, show_col_types = FALSE)
long_df    <- read_tsv(params$long,    show_col_types = FALSE)

LOCI <- c("adk","fumC","gyrB","icd","mdh","purA","recA")

summary_df <- summary_df %>%
  mutate(
    ST_label   = ifelse(is.na(ST) | ST %in% c("-","new_ST"),
                        ifelse(qc_label == "NEW_ST", "Novel ST", "—"),
                        paste0("ST-", ST)),
    st_numeric = suppressWarnings(as.numeric(ST))
  )

QC_LEVELS  <- c("PASS","NEW_ST","LOW_COVERAGE","NEW_ALLELE","FAIL")
QC_COLOURS <- c(PASS="#28a745", NEW_ST="#ffc107",
                LOW_COVERAGE="#fd7e14", NEW_ALLELE="#e83e8c", FAIL="#dc3545")
QC_BG      <- c(PASS="#e8f5e9", NEW_ST="#fff8e1",
                LOW_COVERAGE="#fff1e0", NEW_ALLELE="#fce4ec", FAIL="#ffebee")

qc_counts <- summary_df %>%
  mutate(qc_label = factor(qc_label, levels = QC_LEVELS)) %>%
  count(qc_label, .drop = FALSE) %>%
  mutate(pct = 100 * n / sum(n))

# Per-locus dot colour for a sample: FAIL-red > NEW_ALLELE-pink > LOW-orange > PASS-green
dot_colour <- function(flag, coverage, cov_good = 100, cov_warn = 50) {
  dplyr::case_when(
    flag == "no_hit"        ~ "#dc3545",
    coverage < cov_warn     ~ "#dc3545",
    flag == "new_allele"    ~ "#e83e8c",
    coverage < cov_good     ~ "#fd7e14",
    TRUE                    ~ "#28a745"
  )
}

# Build "● ● ● ● ● ● ●" HTML per sample, one dot per locus (in LOCI order).
# Dots show a tooltip with locus, flag, coverage, identity.
dots_by_sample <- long_df %>%
  mutate(color = dot_colour(flag, coverage),
         tip   = sprintf("%s: %s, cov=%d, id=%.1f%%",
                         locus, flag, coverage, identity)) %>%
  arrange(sample_id, match(locus, LOCI)) %>%
  group_by(sample_id) %>%
  summarise(
    Loci = paste0(
      '<span style="white-space:nowrap">',
      paste(sprintf(
        '<span title="%s" style="display:inline-block;width:12px;height:12px;border-radius:50%%;background:%s;margin-right:2px;vertical-align:middle;border:1px solid rgba(0,0,0,0.1)"></span>',
        tip, color), collapse = ""),
      "</span>"),
    .groups = "drop"
  )

summary_df <- summary_df %>% left_join(dots_by_sample, by = "sample_id")

total_samples <- nrow(summary_df)
# na.rm protects against merge gaps / missing values from upstream
pass_samples  <- sum(summary_df$qc_label == "PASS",          na.rm = TRUE)
low_cov       <- sum(summary_df$qc_label == "LOW_COVERAGE",  na.rm = TRUE)
new_st        <- sum(summary_df$qc_label == "NEW_ST",        na.rm = TRUE)
new_allele    <- sum(summary_df$qc_label == "NEW_ALLELE",    na.rm = TRUE)
fail          <- sum(summary_df$qc_label == "FAIL",          na.rm = TRUE)
pass_rate     <- if (total_samples > 0) 100 * pass_samples / total_samples else 0
unique_sts    <- summary_df %>%
                   filter(qc_label %in% c("PASS","LOW_COVERAGE")) %>%
                   pull(ST) %>% unique() %>% length()
unique_runs   <- n_distinct(summary_df$run_id)

# Semantic colour for the banner + metric cards
if (pass_rate >= 80) {
  banner_class   <- "banner-green"
  gradient_start <- "#28a745"; gradient_end <- "#1e7e34"
  banner_icon    <- "✓"
  banner_verdict <- sprintf("Run succeeded — %d of %d samples (%.0f%%) fully typed.",
                             pass_samples, total_samples, pass_rate)
} else if (pass_rate >= 50) {
  banner_class   <- "banner-amber"
  gradient_start <- "#fd7e14"; gradient_end <- "#d06400"
  banner_icon    <- "⚠"
  banner_verdict <- sprintf("Mixed run — %d of %d (%.0f%%) fully typed; review %d samples below.",
                             pass_samples, total_samples, pass_rate,
                             total_samples - pass_samples)
} else {
  banner_class   <- "banner-red"
  gradient_start <- "#dc3545"; gradient_end <- "#a71d2a"
  banner_icon    <- "✗"
  banner_verdict <- sprintf("Run needs attention — only %d of %d (%.0f%%) fully typed. Check per-locus QC.",
                             pass_samples, total_samples, pass_rate)
}
```

```{css, echo=FALSE}
/* Banner */
.status-banner {
  color: white; padding: 26px 30px; border-radius: 10px;
  margin: 10px 0 24px 0; box-shadow: 0 4px 10px rgba(0,0,0,0.12);
}
.status-banner .verdict {
  font-size: 1.7em; font-weight: 700; margin-bottom: 6px;
}
.status-banner .sub { font-size: 1.05em; opacity: 0.92; }

/* Metric cards */
.metric-grid {
  display: grid; grid-template-columns: repeat(auto-fit, minmax(200px, 1fr));
  gap: 15px; margin: 10px 0 24px 0;
}
.metric-box {
  color: white; padding: 18px 22px; border-radius: 10px;
  box-shadow: 0 4px 6px rgba(0,0,0,0.1);
}
.metric-label { font-size: 1.05em; opacity: 0.92; }
.metric-value { font-size: 2.6em; font-weight: 700; margin: 6px 0; line-height: 1.1; }
.metric-sub   { font-size: 0.95em; opacity: 0.85; }

/* Quality badges */
.qb { display: inline-block; padding: 3px 9px; border-radius: 5px;
      font-weight: 600; font-size: 0.85em; }
.qb-pass  { background:#d4edda; color:#155724; }
.qb-newst { background:#fff3cd; color:#856404; }
.qb-low   { background:#ffe8cc; color:#8a4a00; }
.qb-newal { background:#fce4ec; color:#880e4f; }
.qb-fail  { background:#f8d7da; color:#721c24; }

/* Info panel */
.info-panel {
  background-color: #f1f5f9; border-left: 4px solid #64748b;
  padding: 12px 16px; margin: 16px 0; border-radius: 5px;
  font-size: 0.95em;
}
.interp {
  background: #fff8e1; border-left: 3px solid #ffc107;
  padding: 10px 14px; margin: 10px 0 20px 0; border-radius: 4px;
  font-size: 0.95em;
}
.interp::before { content: "💡 "; }

details summary {
  cursor: pointer; font-weight: 600; padding: 8px 0;
  color: #334155; font-size: 1.05em;
}
details summary:hover { color: #0f172a; }
details[open] summary { margin-bottom: 12px; }
```

# Overview {.unnumbered}

<div class="status-banner" style="background: linear-gradient(135deg, `r gradient_start` 0%, `r gradient_end` 100%);">
  <div class="verdict">`r banner_icon` &nbsp; `r banner_verdict`</div>
  <div class="sub">Report generated `r format(Sys.time(), "%Y-%m-%d %H:%M")` · *E. coli* Achtman 7-locus scheme · `r total_samples` samples across `r unique_runs` run(s).</div>
</div>

```{r metric-cards}
card_colour <- function(rate) {
  if (rate >= 80) c("#28a745","#1e7e34")
  else if (rate >= 50) c("#fd7e14","#d06400")
  else c("#dc3545","#a71d2a")
}
cc <- card_colour(pass_rate)

tagList(
  div(class = "metric-grid",
    div(class = "metric-box",
        style = sprintf("background: linear-gradient(135deg, %s 0%%, %s 100%%);", cc[1], cc[2]),
        div(class = "metric-label", "Fully typed (PASS)"),
        div(class = "metric-value", pass_samples),
        div(class = "metric-sub", sprintf("%.0f%% of %d", pass_rate, total_samples))
    ),
    div(class = "metric-box",
        style = "background: linear-gradient(135deg, #6b7280 0%, #4b5563 100%);",
        div(class = "metric-label", "Total samples"),
        div(class = "metric-value", total_samples),
        div(class = "metric-sub", paste(unique_runs, "run(s)"))
    ),
    div(class = "metric-box",
        style = "background: linear-gradient(135deg, #5a3d8c 0%, #3d2463 100%);",
        div(class = "metric-label", "Unique STs called"),
        div(class = "metric-value", unique_sts),
        div(class = "metric-sub", "includes low-coverage calls")
    ),
    div(class = "metric-box",
        style = sprintf("background: linear-gradient(135deg, %s 0%%, %s 100%%);",
                        ifelse(fail + new_allele > 0, "#dc3545", "#6b7280"),
                        ifelse(fail + new_allele > 0, "#a71d2a", "#4b5563")),
        div(class = "metric-label", "Need attention"),
        div(class = "metric-value", fail + new_allele),
        div(class = "metric-sub", sprintf("%d FAIL, %d NEW_ALLELE", fail, new_allele))
    )
  )
)
```

<div class="info-panel">
**QC labels:**
<span class="qb qb-pass">✓ PASS</span> all 7 loci known at 100% identity, ≥100× coverage, ST in PubMLST &nbsp;·&nbsp;
<span class="qb qb-newst">NEW_ST</span> novel 7-allele combination &nbsp;·&nbsp;
<span class="qb qb-low">LOW_COVERAGE</span> 50–99× on at least one locus &nbsp;·&nbsp;
<span class="qb qb-newal">NEW_ALLELE</span> imperfect BLAST match on at least one locus &nbsp;·&nbsp;
<span class="qb qb-fail">✗ FAIL</span> <50× coverage or no hit
</div>

---

# Per-locus diagnostics

This is the first place to look when samples fail. If a single locus is weak across **most** samples, the problem is upstream (primer, amplification, basecaller) rather than per-sample.

```{r locus-qc-panel, fig.height=4}
locus_stats <- long_df %>%
  group_by(locus) %>%
  summarise(
    n_samples      = n(),
    n_high_cov     = sum(coverage >= 100),
    n_mid_cov      = sum(coverage >= 50 & coverage < 100),
    n_low_cov      = sum(coverage < 50),
    n_known        = sum(flag == "known"),
    n_new_allele   = sum(flag == "new_allele"),
    n_no_hit       = sum(flag == "no_hit"),
    median_cov     = median(coverage),
    .groups = "drop"
  ) %>%
  mutate(
    pct_high = 100 * n_high_cov / n_samples,
    pct_mid  = 100 * n_mid_cov  / n_samples,
    pct_low  = 100 * n_low_cov  / n_samples,
    locus    = factor(locus, levels = LOCI)
  ) %>%
  arrange(locus)

cov_long <- locus_stats %>%
  select(locus, `≥100× (good)` = pct_high,
         `50–99× (warn)`       = pct_mid,
         `<50× (fail)`         = pct_low) %>%
  pivot_longer(-locus, names_to = "band", values_to = "pct") %>%
  mutate(band = factor(band,
                       levels = c("≥100× (good)","50–99× (warn)","<50× (fail)")))

plot_ly(cov_long,
        y = ~locus, x = ~pct, color = ~band,
        type = 'bar', orientation = 'h',
        colors = c("#28a745","#fd7e14","#dc3545"),
        text = ~sprintf("%s — %s: %.0f%%", locus, band, pct),
        hoverinfo = 'text') %>%
  layout(barmode = 'stack',
         title = list(text = "Share of samples meeting each coverage threshold, per locus",
                      font = list(size = 14)),
         xaxis = list(title = "% of samples", ticksuffix = "%", range = c(0,100)),
         yaxis = list(title = "", categoryorder = "array", categoryarray = rev(LOCI)),
         legend = list(orientation = "h", x = 0.02, y = -0.15))
```

```{r locus-interp, results='asis'}
weak_loci <- locus_stats %>% filter(pct_low > 25) %>% pull(locus) %>% as.character()
flagged_loci <- locus_stats %>% filter(n_new_allele > 0 | n_no_hit > 0) %>%
                pull(locus) %>% as.character()

msg <- if (length(weak_loci) == 0 && length(flagged_loci) == 0) {
  "All 7 loci performed acceptably across this run. Individual FAIL/NEW_ALLELE calls are per-sample, not systemic."
} else {
  paste0(
    if (length(weak_loci) > 0) sprintf(
      "**%s** had <50× coverage in >25%% of samples — check the primer stock, amplification conditions, or read-length filtering for this locus. ",
      paste(weak_loci, collapse = ", ")) else "",
    if (length(flagged_loci) > 0) sprintf(
      "Imperfect BLAST matches were observed for **%s**; these may be genuinely novel alleles or basecalling artefacts worth verifying on a higher-accuracy model.",
      paste(flagged_loci, collapse = ", ")) else ""
  )
}
cat('<div class="interp">', msg, '</div>', sep = "")
```

---

# Samples needing attention

Prioritised list — FAIL and NEW_ALLELE first. LOW_COVERAGE samples still have an ST call but one or more loci are undercovered.

The **Loci** column shows a quick 7-dot summary (adk · fumC · gyrB · icd · mdh · purA · recA). Hover a dot for details.
<span style="display:inline-block;width:11px;height:11px;border-radius:50%;background:#28a745;vertical-align:middle;border:1px solid rgba(0,0,0,0.1)"></span> known & ≥100× &nbsp;·&nbsp;
<span style="display:inline-block;width:11px;height:11px;border-radius:50%;background:#fd7e14;vertical-align:middle;border:1px solid rgba(0,0,0,0.1)"></span> known & 50–99× &nbsp;·&nbsp;
<span style="display:inline-block;width:11px;height:11px;border-radius:50%;background:#e83e8c;vertical-align:middle;border:1px solid rgba(0,0,0,0.1)"></span> new allele &nbsp;·&nbsp;
<span style="display:inline-block;width:11px;height:11px;border-radius:50%;background:#dc3545;vertical-align:middle;border:1px solid rgba(0,0,0,0.1)"></span> <50× / no hit

```{r attention-table}
attn <- summary_df %>%
  filter(qc_label %in% c("FAIL","NEW_ALLELE","LOW_COVERAGE","NEW_ST")) %>%
  mutate(
    priority = match(qc_label, c("FAIL","NEW_ALLELE","LOW_COVERAGE","NEW_ST")),
    ST = ST_label
  ) %>%
  arrange(priority) %>%
  select(any_of(c("sample_id","run_id","barcode","sample_type",
                  "qc_label","ST","Loci","qc_notes",
                  "adk","fumC","gyrB","icd","mdh","purA","recA")))

if (nrow(attn) > 0) {
  datatable(
    attn, rownames = FALSE, filter = "top",
    escape = FALSE,
    extensions = "Buttons",
    options = list(pageLength = 15, scrollX = TRUE, dom = 'Bfrtip',
                   buttons = c('copy','csv','excel'),
                   columnDefs = list(
                     list(className = 'dt-center', targets = which(names(attn) == "Loci") - 1)
                   ))
  ) %>%
    formatStyle("qc_label", target = "row",
                backgroundColor = styleEqual(QC_LEVELS, QC_BG)) %>%
    formatStyle("qc_label", fontWeight = "bold",
                color = styleEqual(QC_LEVELS, QC_COLOURS))
} else {
  cat('<div class="interp">✓ No samples need review — every sample PASSed cleanly.</div>')
}
```

```{r attention-interp, results='asis'}
actions <- c()
if (fail > 0)        actions <- c(actions, sprintf("**%d FAIL** → resequence (low coverage) or check barcode assignment", fail))
if (new_allele > 0)  actions <- c(actions, sprintf("**%d NEW_ALLELE** → review BLAST identity; if confirmed novel, submit to PubMLST", new_allele))
if (low_cov > 0)     actions <- c(actions, sprintf("**%d LOW_COVERAGE** → ST is likely correct but some loci undersampled; verify if publishing", low_cov))
if (new_st > 0)      actions <- c(actions, sprintf("**%d NEW_ST** → all alleles known but combination is novel; candidate PubMLST submission", new_st))
if (length(actions) > 0) {
  cat('<div class="interp">Suggested actions: ', paste(actions, collapse = " · "), '</div>', sep = "")
}
```

---

# Successful STs

```{r qc-dist, fig.height=4}
plot_ly(qc_counts %>% filter(n > 0),
        labels = ~qc_label, values = ~n,
        type = 'pie', textposition = 'inside', textinfo = 'label+percent',
        marker = list(colors = QC_COLOURS[levels(qc_counts$qc_label)],
                      line = list(color = '#ffffff', width = 2)),
        hoverinfo = 'text',
        text = ~sprintf("%s: %d samples (%.1f%%)", qc_label, n, pct)) %>%
  layout(title = list(text = "QC label distribution", font = list(size = 14)),
         showlegend = TRUE, margin = list(t = 40, b = 20))
```

## ST frequency

```{r st-bar, fig.height=4.5}
st_counts <- summary_df %>%
  filter(!is.na(st_numeric)) %>%
  count(st_numeric, sort = TRUE) %>%
  head(20) %>%
  mutate(st_label = paste0("ST-", st_numeric))

if (nrow(st_counts) > 0) {
  plot_ly(st_counts,
          x = ~reorder(st_label, n), y = ~n,
          type = 'bar',
          marker = list(color = ~n, colorscale = 'Viridis', showscale = FALSE),
          text = ~sprintf("ST-%s: %d samples", st_numeric, n),
          hoverinfo = 'text') %>%
    layout(title = list(text = "Top sequence types (by sample count)",
                        font = list(size = 14)),
           xaxis = list(title = "Sequence Type", tickangle = -45),
           yaxis = list(title = "Samples"),
           margin = list(b = 60))
} else {
  cat('<div class="interp">No known STs were called in this run.</div>')
}
```

```{r st-interp, results='asis'}
if (nrow(st_counts) > 0) {
  top <- st_counts[1, ]
  more_than_one <- sum(st_counts$n > 1)
  msg <- sprintf(
    "The most frequent ST in this run is **ST-%s** (%d samples). %d ST%s appeared in more than one sample — a signal of related isolates.",
    top$st_numeric, top$n, more_than_one, ifelse(more_than_one == 1, "", "s")
  )
  cat('<div class="interp">', msg, '</div>', sep = "")
}
```

## ST × sample type

```{r type-breakdown, fig.height=4}
if ("sample_type" %in% colnames(summary_df) && any(!is.na(summary_df$sample_type))) {
  type_qc <- summary_df %>%
    mutate(qc_label = factor(qc_label, levels = QC_LEVELS)) %>%
    count(sample_type, qc_label, .drop = FALSE) %>%
    group_by(sample_type) %>% mutate(pct = 100 * n / sum(n)) %>% ungroup()

  plot_ly(type_qc,
          x = ~sample_type, y = ~n, color = ~qc_label,
          colors = QC_COLOURS,
          type = 'bar',
          text = ~sprintf("%s — %s: %d (%.1f%%)", sample_type, qc_label, n, pct),
          hoverinfo = 'text') %>%
    layout(title = list(text = "QC outcomes by sample type", font = list(size = 14)),
           barmode = 'stack',
           xaxis = list(title = "Sample type"),
           yaxis = list(title = "Samples"),
           legend = list(title = list(text = "QC")))
} else {
  cat('<div class="interp">No sample_type column present.</div>')
}
```

---

# Complete results table

Every sample in the run — use the filter boxes to narrow down.

```{r full-table}
disp <- summary_df %>%
  mutate(ST = ST_label) %>%
  select(any_of(c("sample_id","run_id","barcode","collection_date","sample_type",
                  "ST","Loci","adk","fumC","gyrB","icd","mdh","purA","recA",
                  "qc_label","qc_notes")))

datatable(
  disp, rownames = FALSE, filter = "top",
  escape = FALSE,
  extensions = "Buttons",
  options = list(pageLength = 25, scrollX = TRUE, searchHighlight = TRUE,
                 dom = 'Bfrtip', buttons = c('copy','csv','excel'))
) %>%
  formatStyle("qc_label", target = "row",
              backgroundColor = styleEqual(QC_LEVELS, QC_BG)) %>%
  formatStyle("ST", fontWeight = "bold", color = "#5a3d8c")
```

---

# Advanced

<details>
<summary>Allele heatmap (top STs × 7 loci)</summary>

```{r allele-heatmap, fig.height=7}
top_st_ids <- summary_df %>%
  filter(qc_label %in% c("PASS","LOW_COVERAGE"), !is.na(st_numeric)) %>%
  count(st_numeric, sort = TRUE) %>% head(30) %>% pull(st_numeric)

allele_mat <- summary_df %>%
  filter(st_numeric %in% top_st_ids) %>%
  select(st_numeric, all_of(LOCI)) %>% distinct() %>% arrange(st_numeric) %>%
  mutate(st_label = paste0("ST-", st_numeric)) %>%
  select(-st_numeric) %>% column_to_rownames("st_label") %>%
  mutate(across(everything(), ~ suppressWarnings(as.numeric(.))))

if (nrow(allele_mat) >= 1) {
  plot_ly(z = as.matrix(allele_mat),
          x = colnames(allele_mat), y = rownames(allele_mat),
          type = "heatmap", colorscale = "Viridis",
          colorbar = list(title = "Allele #"),
          text = as.matrix(allele_mat),
          hovertemplate = 'ST: %{y}<br>Locus: %{x}<br>Allele: %{z}<extra></extra>') %>%
    layout(xaxis = list(title = "Locus"),
           yaxis = list(title = "Sequence type"),
           margin = list(l = 100))
} else {
  cat('_Not enough known STs to build a heatmap._')
}
```
</details>

<details>
<summary>Per-locus detail (every sample × locus)</summary>

```{r long-table}
datatable(long_df, rownames = FALSE, filter = "top",
          extensions = "Buttons",
          options = list(pageLength = 25, scrollX = TRUE, dom = 'Bfrtip',
                         buttons = c('copy','csv','excel')))
```
</details>

<details>
<summary>Coverage vs identity (all samples × loci)</summary>

```{r cov-ident, fig.height=5}
long_df %>%
  mutate(status = case_when(
    flag == "known"       ~ "known allele",
    flag == "new_allele"  ~ "potential new allele",
    flag == "no_hit"      ~ "no BLAST hit",
    TRUE                  ~ flag
  )) %>%
  plot_ly(x = ~coverage, y = ~identity, color = ~status,
          text = ~paste0(sample_id, " / ", locus),
          type = "scatter", mode = "markers",
          marker = list(size = 9, opacity = 0.75)) %>%
  layout(xaxis = list(title = "Primer-based read coverage (cutadapt)"),
         yaxis = list(title = "BLAST percent identity", range = c(90, 101)))
```
</details>

<details>
<summary>Methods</summary>

**MLST typing** uses the PubMLST *Escherichia coli* Achtman 7-locus scheme (adk, fumC, gyrB, icd, mdh, purA, recA; <https://pubmlst.org/escherichia/>).

**Consensus generation** — per-barcode fastq are concatenated, then medaka (model `r1041_e82_400bps_sup_v5.0.0`) builds a per-gene consensus against a 7-gene concatenated reference.

**Allele calling** — consensus contigs are BLASTed against each locus's PubMLST allele FASTA. A locus is *known* if the best hit covers the full allele length at 100% identity; otherwise flagged as a potential *new allele*.

**Primer coverage QC** — cutadapt scans reads for the 5' (`-g`) and 3' (`-a`) primers at error rate 0.1; reads with both primers are counted as the coverage metric. <50× triggers FAIL for that locus; 50–99× triggers LOW_COVERAGE.

**ST assignment** — the 7 called alleles are joined to the PubMLST profile table. Exact match → ST; otherwise `NEW_ST`.

**QC label priority** — FAIL > LOW_COVERAGE > NEW_ALLELE > NEW_ST > PASS. The most severe condition wins.
</details>

<details>
<summary>Session info (for reproducibility)</summary>

```{r session}
sessionInfo()
```
</details>

---

<div style="color:#64748b; font-size:0.9em; text-align:center; margin: 30px 0 15px 0; border-top: 1px solid #e2e8f0; padding-top: 15px;">
  ONT-MLST pipeline <strong>v`r params$version`</strong> · commit <code>`r params$commit`</code> · report generated `r format(Sys.time(), "%Y-%m-%d %H:%M:%S %Z")`
  <br>
  Samplesheet: <code>`r basename(params$summary)`</code> · <em>E. coli</em> Achtman 7-locus scheme
</div>
